GEE models

### 2016-07-27 doc/manuscript.Rmd
Updated manuscript to reflect new proj style

```{r knit_setup, echo=FALSE}
knitr::opts_knit$set(root.dir = '../')
```

```{r setup, message=FALSE, echo=FALSE}
source('.Rprofile')
suppressMessages(run_setup())
ds <- load_data()
ds0yr <- filter(ds, VN == 0)
```

```{r caption_setup}
## Include captions below using `captioner` package
fig <- captioner(prefix = 'Fig.')
cite_f <- pryr::partial(fig, display = 'cite')
sfig <- captioner(prefix = 'ESM Fig.')
cite_sf <- pryr::partial(sfig, display = 'cite')
tab <- captioner(prefix = 'Table')
cite_t <- pryr::partial(tab, display = 'cite')
stab <- captioner(prefix = 'ESM Table')
cite_st <- pryr::partial(stab, display = 'cite')
# usage: cite_st('basicChar')

@@

```{r lcmmPls, cache=TRUE, results='hide'}
# include also the 3-yr and 6-yr data for training/testing.
lcmm_results <- analyze_lcmm(ds)
lcmm_data <- combine_lcmm_data(ds, lcmm_results)
plsda_results <- analyze_plsda(lcmm_data)
plsda_dysgly <- dysgly_data %>% 
    mutate(ConvertDysgly = factor(ConvertDysgly, levels = c(0, 1), labels = c('No', 'Yes'))) %>% 
    analyze_plsda('ConvertDysgly')
```

@@

```{r ESM_Table1}
prep_qic <- gee_df %>%
    dplyr::select(
        SID, VN, lISSI2, lISI, TotalNE, Sex, Ethnicity, MET, ALT, BaseAge,
        Waist, BMI, AlcoholPerWk, TobaccoUse, FamHistDiab
        )

qic_is <- prep_qic %>% 
    dplyr::select(-lISSI2) %>% 
    na.omit()

qic_bcf <- prep_qic %>% 
    dplyr::select(-lISI) %>% 
    na.omit()

# QIC for IS
M0 <- geepack::geeglm(
    lISI ~ TotalNE + VN, data = qic_is,
    id = SID, family = gaussian,
    corstr = 'ar1'
    )

M1 <- update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex)
M2 <- update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT) # best
M3 <- update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + MET) # best
M4 <- update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + MET + AlcoholPerWk) # best
M5 <- update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + MET + AlcoholPerWk + FamHistDiab) # best
M6 <- update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + MET + AlcoholPerWk + FamHistDiab + TobaccoUse) # best
M7 <- update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + FamHistDiab + TobaccoUse) # best
M8 <- update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + FamHistDiab) # best
M9 <- update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + FamHistDiab + TotalNE:VN)

qic_is_tab <- MuMIn::model.sel(M0, M1, M2, M3, M4, M5, M6, M7, M8, M9, rank = QIC) %>% 
    dplyr::add_rownames() %>%
    dplyr::select(Model = rowname, QIC, Delta = delta) %>%
    dplyr::mutate(id = seq_len(nrow(.))) %>%
    dplyr::bind_rows(., data.frame(Model = '**log(ISI)**', id = 0.5))

# QIC data for BCF
qic_bcf <- prep_qic %>% 
    dplyr::select(-lISI) %>% 
    na.omit()

M0 <- geepack::geeglm(
    lISSI2 ~ TotalNE + VN, data = qic_bcf,
    id = SID, family = gaussian,
    corstr = 'ar1'
    )
M1 <- update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex)
M2 <- update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT) 
M3 <- update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + MET)
M4 <- update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + MET + AlcoholPerWk)
M5 <- update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + MET + AlcoholPerWk + FamHistDiab) # best
M6 <- update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + MET + AlcoholPerWk + FamHistDiab + TobaccoUse) # best
M7 <- update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + FamHistDiab + TobaccoUse) # best
M8 <- update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + FamHistDiab) # best
M9 <- update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + FamHistDiab + TotalNE:VN) # best

qic_bcf_tab <- MuMIn::model.sel(M0, M1, M2, M3, M4, M5, M6, M7, M8, M9, rank = QIC) %>% 
    dplyr::add_rownames() %>%
    dplyr::select(Model = rowname, QIC, Delta = delta) %>% 
    dplyr::mutate(id = seq_len(nrow(.))+10) %>%
    dplyr::bind_rows(., data.frame(Model = '**log(ISSI-2)**', id = 10.5))

>>>>

```{r knit_setup, echo=FALSE}
#knitr::opts_knit$set(root.dir = '../')
```

```{r setup, message=FALSE, echo=FALSE}
#source('.Rprofile')
devtools::load_all()
set_options()
ds <- project_data
ds0yr <- dplyr::filter(ds, VN == 0)
```

```{r caption_setup}
## Include captions below using `captioner` package
library(captioner)
fig <- captioner(prefix = 'Fig.')
cite_f <- pryr::partial(fig, display = 'cite')
sfig <- captioner(prefix = 'ESM Fig.')
cite_sf <- pryr::partial(sfig, display = 'cite')
tab <- captioner(prefix = 'Table')
cite_t <- pryr::partial(tab, display = 'cite')
stab <- captioner(prefix = 'ESM Table')
cite_st <- pryr::partial(stab, display = 'cite')
# usage: cite_st('basicChar')

@@

```{r lcmmPls, cache=TRUE, results='hide'}
# include also the 3-yr and 6-yr data for training/testing.
lcmm_results <- analyze_lcmm(ds)
lcmm_data <- combine_lcmm_data(ds, lcmm_results)
plsda_results <- analyze_plsda(lcmm_data)
plsda_dysgly <- dysgly_data %>% 
    dplyr::mutate(ConvertDysgly = factor(ConvertDysgly, levels = c(0, 1), labels = c('No', 'Yes'))) %>% 
    analyze_plsda('ConvertDysgly')
```

@@

```{r ESM_Table1}
library(magrittr)
prep_qic <- gee_df %>%
    dplyr::select(
        SID, VN, lISSI2, lISI, TotalNE, Sex, Ethnicity, MET, ALT, BaseAge,
        Waist, BMI, AlcoholPerWk, TobaccoUse, FamHistDiab
        )

qic_is <- prep_qic %>% 
    dplyr::select(-lISSI2) %>% 
    stats::na.omit()

qic_bcf <- prep_qic %>% 
    dplyr::select(-lISI) %>% 
    stats::na.omit()

# QIC for IS
M0 <- geepack::geeglm(
    lISI ~ TotalNE + VN, data = qic_is,
    id = SID, family = stats::gaussian,
    corstr = 'ar1'
    )

M1 <- stats::update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex)
M2 <- stats::update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT) # best
M3 <- stats::update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + MET) # best
M4 <- stats::update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + MET + AlcoholPerWk) # best
M5 <- stats::update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + MET + AlcoholPerWk + FamHistDiab) # best
M6 <- stats::update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + MET + AlcoholPerWk + FamHistDiab + TobaccoUse) # best
M7 <- stats::update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + FamHistDiab + TobaccoUse) # best
M8 <- stats::update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + FamHistDiab) # best
M9 <- stats::update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + FamHistDiab + TotalNE:VN)

qic_is_tab <- MuMIn::model.sel(M0, M1, M2, M3, M4, M5, M6, M7, M8, M9, rank = MuMIn::QIC) %>% 
    tibble::rownames_to_column() %>%
    dplyr::select(Model = rowname, QIC = IC, Delta = delta) %>%
    dplyr::mutate(id = seq_len(nrow(.))) %>%
    dplyr::bind_rows(., data.frame(Model = '**log(ISI)**', id = 0.5))

# QIC data for BCF
qic_bcf <- prep_qic %>% 
    dplyr::select(-lISI) %>% 
    stats::na.omit()

M0 <- geepack::geeglm(
    lISSI2 ~ TotalNE + VN, data = qic_bcf,
    id = SID, family = stats::gaussian,
    corstr = 'ar1'
    )
M1 <- stats::update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex)
M2 <- stats::update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT) 
M3 <- stats::update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + MET)
M4 <- stats::update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + MET + AlcoholPerWk)
M5 <- stats::update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + MET + AlcoholPerWk + FamHistDiab) # best
M6 <- stats::update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + MET + AlcoholPerWk + FamHistDiab + TobaccoUse) # best
M7 <- stats::update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + FamHistDiab + TobaccoUse) # best
M8 <- stats::update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + FamHistDiab) # best
M9 <- stats::update(M0, . ~ . + Waist + BaseAge + Ethnicity + Sex + ALT + FamHistDiab + TotalNE:VN) # best

qic_bcf_tab <- MuMIn::model.sel(M0, M1, M2, M3, M4, M5, M6, M7, M8, M9, rank = MuMIn::QIC) %>% 
    tibble::rownames_to_column() %>%
    dplyr::select(Model = rowname, QIC = IC, Delta = delta) %>% 
    dplyr::mutate(id = seq_len(nrow(.))+10) %>%
    dplyr::bind_rows(., data.frame(Model = '**log(ISSI-2)**', id = 10.5))
